The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-10-07 paper.tex
Added data section to CCCC

\title{The perceptual dimensions of \\ sonority-driven epenthesis}
\author{Michelle A. Fullwood}
\date{Generals Paper, MIT \\ September 2013}
\begin{document}

@@

\begin{longtable}{ccccc}
	& Underlying form      & Surface form & {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) & {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) \\ \hline
    \multicolumn{5}{c}{Fall-\{Rise, Plateau\}: [CC\textipa{1}C]} \\ \hline
	a. & \textipa{j@-rk't'-o} & \textipa{j@nk'1t'o} & 2.36 & 1.37 \\
	b. & \textipa{j@-rks-o}   & \textipa{j@nk1so}   & 2.36 & 0.59 \\
    c. & \textipa{j@-rk'm-o}  & \textipa{j@nk'1mo}  & 2.36 & 0.27 \\
    d. & \textipa{j@-\underline{wzf}-o} & \textipa{j@wz1fo} & 2.03 & 1.33 \\
	e. & \textipa{j@-mxr-o}   & \textipa{j@mx1ro}   & 2.03 & 0.22 \\
    f. & \textipa{j@-\underline{sgd}-o} & \textipa{j@sg1do}   & 2.11 & 1.37 \\  
    g. & \textipa{j@-sdB-o}   & \textipa{j@sd1Bo}   & 2.11 & 0.18 \\ \hline
    \multicolumn{5}{c}{\{Rise, Plateau\}-\{Rise, Plateau\}: [CC\textipa{1}C]} \\ \hline
    h. & \textipa{j@-\underline{gdf}-o} & \textipa{j@gd1fo} & 1.37 & 0.59 \\
    i. & \textipa{j@-\underline{gdr}-o} & \textipa{j@gd1ro} & 1.37 & 0.12 \\
    j. & \textipa{j@-\underline{kmr}-o} & \textipa{j@km1ro} & 0.27 & 0.46 \\
    k. & \textipa{j@-\underline{sfr}-o} & \textipa{j@sf1ro} & 1.33 & 0.22 \\
    l. & \textipa{j@-\underline{sBr}-o} & \textipa{j@sB1ro} & 0.34 & 0.73 \\ \hline
    \multicolumn{5}{c}{Fall-Fall: [CC\textipa{1}C]} \\ \hline
    m. & \textipa{j@-rfk-o} & \textipa{j@nf1ko} & 2.03 & 2.11 \\ 
    n. & \textipa{j@-rmd-o} & \textipa{j@rm1do} & 1.89 & 2.36 \\ 
    o. & \textipa{j-a-mst-o}& \textipa{jams1to} & 2.03 & 2.11 \\ \hline
    \multicolumn{5}{c}{\{Rise,Plateau\}-Fall: [C\textipa{1}CC]} \\ \hline
    p. & \textipa{j@-kft-o} & \textipa{j@k1fto} & 0.59 & 2.11 \\
    q. & \textipa{j@-dmd-o} & \textipa{j@d1mdo} & 0.27 & 2.36 \\
    r. & \textipa{j@-drs-o} & \textipa{j@d1rso} & 0.12 & 2.21 \\ 
    s. & \textipa{j@-\underline{k'rm}-o} & \textipa{j@k'1rmo} & 0.12 & 1.89 \\ 
    t. & \textipa{j@-\underline{srB}-o}  & \textipa{j@s1rBo}  & 0.22 & 1.57 \\
    u. & \textipa{j@-frt-o} & \textipa{j@f1rto} & 0.22 & 2.36 \\
    v. & \textipa{j@-sBx-o} & \textipa{j@s1Bxo} & 0.34 & 2.17 \\
    w. & \textipa{j-a-mrg-o} & \textipa{jam1rgo} & 0.46 & 2.36 \\ \hline
    \multicolumn{5}{c}{Non-jussive forms} \\ \hline
    x. & \textipa{j-t-Bt'@b@t'} & \textipa{j1t1Bt'@b@t'} & 0.18 & 2.38 \\
    y. & \textipa{j-t-rs@n@s} & \textipa{j1t1rs@n@s} & 0.12 & 2.21 \\
    z. & \textipa{j-t-kB@s@s} & \textipa{j1tk1B@s@s} & 1.37 & 0.12 \\
    A. & \textipa{j-t-k't'@k'@t'} & \textipa{j1tk'1t'@k'@t'} & 1.37 & 1.37 \\
\end{longtable}

@@

\begin{longtable}{ccccc}
	& Underlying form      & Surface form & {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) & {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) \\ \hline
    \multicolumn{5}{c}{Fall-\{Rise, Plateau\}: [CC\textipa{1}C]} \\ \hline
	a. & \textipa{j@-rk't'-o} & \textipa{j@nk'1t'o} & 2.36 & 1.37 \\
	b. & \textipa{j@-rks-o}   & \textipa{j@nk1so}   & 2.36 & 0.59 \\
    c. & \textipa{j@-rk'm-o}  & \textipa{j@nk'1mo}  & 2.36 & 0.27 \\
    d. & \textipa{j@-\underline{wzf}-o} & \textipa{j@wz1fo} & 2.03 & 1.33 \\
	e. & \textipa{j@-mxr-o}   & \textipa{j@mx1ro}   & 2.03 & 0.22 \\
    f. & \textipa{j@-\underline{sgd}-o} & \textipa{j@sg1do}   & 2.11 & 1.37 \\  
    g. & \textipa{j@-sdB-o}   & \textipa{j@sd1Bo}   & 2.11 & 0.18 \\ \hline
    \multicolumn{5}{c}{\{Rise, Plateau\}-\{Rise, Plateau\}: [C\textipa{1}CC]} \\ \hline
    h. & \textipa{j@-\underline{gdf}-o} & \textipa{j@g1dfo} & 1.37 & 0.59 \\
    i. & \textipa{j@-\underline{gdr}-o} & \textipa{j@g1dro} & 1.37 & 0.12 \\
    j. & \textipa{j@-\underline{kmr}-o} & \textipa{j@k1mro} & 0.27 & 0.46 \\
    k. & \textipa{j@-\underline{sfr}-o} & \textipa{j@s1fro} & 1.33 & 0.22 \\
    l. & \textipa{j@-\underline{sBr}-o} & \textipa{j@s1Bro} & 0.34 & 0.73 \\ \hline
    \multicolumn{5}{c}{Fall-Fall: [CC\textipa{1}C]} \\ \hline
    m. & \textipa{j@-rfk-o} & \textipa{j@nf1ko} & 2.03 & 2.11 \\ 
    n. & \textipa{j@-rmd-o} & \textipa{j@rm1do} & 1.89 & 2.36 \\ 
    o. & \textipa{j-a-mst-o}& \textipa{jams1to} & 2.03 & 2.11 \\ \hline
    \multicolumn{5}{c}{\{Rise,Plateau\}-Fall: [C\textipa{1}CC]} \\ \hline
    p. & \textipa{j@-kft-o} & \textipa{j@k1fto} & 0.59 & 2.11 \\
    q. & \textipa{j@-dmd-o} & \textipa{j@d1mdo} & 0.27 & 2.36 \\
    r. & \textipa{j@-drs-o} & \textipa{j@d1rso} & 0.12 & 2.21 \\ 
    s. & \textipa{j@-\underline{k'rm}-o} & \textipa{j@k'1rmo} & 0.12 & 1.89 \\ 
    t. & \textipa{j@-\underline{srB}-o}  & \textipa{j@s1rBo}  & 0.22 & 1.57 \\
    u. & \textipa{j@-frt-o} & \textipa{j@f1rto} & 0.22 & 2.36 \\
    v. & \textipa{j@-sBx-o} & \textipa{j@s1Bxo} & 0.34 & 2.17 \\
    w. & \textipa{j-a-mrg-o} & \textipa{jam1rgo} & 0.46 & 2.36 \\ \hline
\end{longtable}

@@

	\node (TR) at (0.124354994547*8, 1) {TR};
	\node (Tb) at (0.183110817262*8, 0.5) {T\textipa{B}};
	\node (FR) at (0.218668945874*8, 1) {FR};
	\node (TN) at (0.266252049151*8, 1.5) {TN};
	\node (Fb) at (0.343023940421*8, 1) {F\textipa{B}};
	\node (NR) at (0.463647609001*8, 1) {NR};
	\node (FN) at (0.540419500271*8, 0.5) {FN};
	\node (TF) at (0.588002603548*8, 1) {TF};
	\node (bR) at (0.726642340682*8, 0.5) {\textipa{B}R};
	\node (Nb) at (0.785398163397*8, 1) {N\textipa{B}};
	\node (RR) at (1.10714871779*8, 1) {RR};
	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
	\node (NN) at (1.2490457724*8, 1) {NN};
	\node (FF) at (1.32581766367*8, 1.5) {FF};
	\node (TT) at (1.37340076695*8, 1) {TT};
	\node (Rb) at (1.57079632679*8, 1) {R\textipa{B}};
	\node (bN) at (1.65393755868*8, 0.5) {\textipa{B}N};
	\node (RN) at (1.84*8, 1) {RN}; %1.89254688119
	\node (NF) at (2.0344439358*8, 1) {NF};
%	\node (GF) at (2.0344439358*8, 1.5) {GF};
	\node (FT) at (2.11121582707*8, 0.5) {FT};
	\node (bF) at (2.17308367293*8, 1) {\textipa{B}F};
	\node (RF) at (2.21429743559*8, 1.5) {RF};
	\node (RT) at (2.35619449019*8, 1) {RT};
	\node (NT) at (2.35619449019*8, 0.5) {NT};
	\node (bT) at (2.38057989937*8, 1.5) {\textipa{B}T};
  \node (rising) at (0.3*8,2.3) {\underline{Rising sonority}};
  \node (level) at (1.2*8,2.3) {\underline{Level sonority}};
  \node (falling) at (2.2*8,2.3) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,0) {};
  \node (axisend)   at (2.7*8,0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
  \node (0pointlabel) at (0.0,-0.5) {0};
  \node (1pointlabel) at (1.0*8,-0.5) {1};
  \node (2pointlabel) at (2.0*8,-0.5) {2};
  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
  % dividing line
  \node (dividinglinestart) at (1.9 * 8,2) {};
  \node (dividinglineend)   at (1.9 * 8,-0.3) {};
  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
  \node (dividingpointlabel) at (1.9*8, -0.5) {1.9};
  \node (dividingpointlabel2) at (1.9*8, -1.0) {\ref{CRNidiolect}};
  % another dividing line
  \node (dividingline2start) at (1.5 * 8,2) {};
  \node (dividingline2end)   at (1.5 * 8,-0.3) {};
  \path [line,dashed] (dividingline2start) -- (dividingline2end) -- cycle;
  \node (dividingpoint2label) at (1.5*8, -0.5) {1.5};
  \node (dividingpoint2label2) at (1.5*8, -1.0) {\ref{defaultCCCidiolect} \& \ref{C1CCidiolect}};
  % third dividing line
  \node (dividingline3start) at (1.0 * 8,2) {};
  \node (dividingline3end)   at (1.0 * 8,-0.3) {};
  \path [line,dashed] (dividingline3start) -- (dividingline3end) -- cycle;
  \node (dividingpoint3label2) at (1.0*8, -1.0) {\ref{wizfidiolect}};
\end{tikzpicture}
}

@@

\bigskip
\resizebox{\linewidth}{!}{
\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
  \tikzstyle{line} = [draw, -latex']
  \node (RT) at (2.5*8, 0)  {RT};
  \node (NT) at (1.67*8,0)  {NT};
  \node (FT) at (1.25*8,0)  {FT};
  \node (TT) at (1*8,-0.5)     {TT};
  \node (RF) at (2*8,0)     {RF};
  \node (NF) at (1.33*8,-0.5)  {NF};
  \node (FF) at (1*8,0)   {FF};
  \node (TF) at (0.8*8,-0.5)   {TF};
  \node (RN) at (1.5*8,0)   {RN};
  \node (NN) at (1*8,0.5)     {NN};
  \node (FN) at (0.75*8,0)  {FN};
  \node (TN) at (0.6*8,0)   {TN};
  \node (RR) at (1*8,1.0)  {RR};
  \node (NR) at (0.67*8,-0.5)  {NR};
  \node (FR) at (0.5*8,0)   {FR};
  \node (TR) at (0.4*8,0)   {TR};
  \node (rising) at (0.5*8,2) {\underline{Rising sonority}};
  \node (level) at (1*8,2) {\underline{Level sonority}};
  \node (falling) at (1.67*8,2) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,-1.0) {};
  \node (axisend)   at (2.7*8,-1.0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, -1.2) -- (0.0*8, -0.8) -- cycle;
  \draw (1.0*8, -1.2) -- (1.0*8, -0.8) -- cycle;
  \draw (2.0*8, -1.2) -- (2.0*8, -0.8) -- cycle;
  \node (0pointlabel) at (0.0,-1.5) {0};
  \node (1pointlabel) at (1.0*8,-1.5) {1};
  \node (2pointlabel) at (2.0*8,-1.5) {2};
  \node (xaxislabel) at (2.7*8,-1.5) {\textsc{SonRise}};
\end{tikzpicture}
}
\bigskip

@@

In this section, I will demonstrate that the rankings already obtained for CCC clusters predict almost exactly which of the CCCC clusters should display variation and in which direction.

@@

Therefore, the only two possible solutions under my approach are [CC\textipa{1}CC] and [C\textipa{1}CC\textipa{1}C]. Which one is chosen depends on the sonority profile of the clusters, and which of {\sc Align-Left} and {\sc Anchor-Left Root} is dominant.

@@

\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c:c|} \hline 
\multicolumn{3}{|c||}{Input:~/\textipa{n-\textnormal{CCC}-n@}/} & Align-Left & Anchor-Left Root \\[0.5ex]
\hline \hline a. & & \textipa{n1\textnormal{C.C}1\textnormal{C}.n@} & 2,3,5,6 & $\ast$ \\
\hline b. & \ding{43} & \textipa{n1.\textnormal{C}1\textnormal{C.C}1.n@} & 2,4!,5,7 & \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}

@@

In this paper, I argued for sonority contour faithfulness being the right way to analyse sonority-driven epenthesis, giving case studies in Irish and Chaha as examples. I additionally proposed that sonority contour distance should be computed by a metric that obeys two desiderata, % TODO

@@

>>>>

\title{The perceptual dimensions of \\ sonority-driven epenthesis}
\author{Michelle A. Fullwood}
\date{Generals Paper, MIT \\ October 2013}
\begin{document}

@@

\begin{tabular}{ccccc}
	& Underlying form      & Surface form & {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) & {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) \\ \hline
    \multicolumn{5}{c}{Fall-\{Rise, Plateau\}: [CC\textipa{1}C]} \\ \hline
	a. & \textipa{j@-rk't'-o} & \textipa{j@nk'1t'o} & 2.36 & 1.37 \\
	b. & \textipa{j@-rks-o}   & \textipa{j@nk1so}   & 2.36 & 0.59 \\
    c. & \textipa{j@-rk'm-o}  & \textipa{j@nk'1mo}  & 2.36 & 0.27 \\
    d. & \textipa{j@-\underline{wzf}-o} & \textipa{j@wz1fo} & 2.03 & 1.33 \\
	e. & \textipa{j@-mxr-o}   & \textipa{j@mx1ro}   & 2.03 & 0.22 \\
    f. & \textipa{j@-\underline{sgd}-o} & \textipa{j@sg1do}   & 2.11 & 1.37 \\  
    g. & \textipa{j@-sdB-o}   & \textipa{j@sd1Bo}   & 2.11 & 0.18 \\ \hline
    \multicolumn{5}{c}{\{Rise, Plateau\}-\{Rise, Plateau\}: [CC\textipa{1}C]} \\ \hline
    h. & \textipa{j@-\underline{gdf}-o} & \textipa{j@gd1fo} & 1.37 & 0.59 \\
    i. & \textipa{j@-\underline{gdr}-o} & \textipa{j@gd1ro} & 1.37 & 0.12 \\
    j. & \textipa{j@-\underline{kmr}-o} & \textipa{j@km1ro} & 0.27 & 0.46 \\
    k. & \textipa{j@-\underline{sfr}-o} & \textipa{j@sf1ro} & 1.33 & 0.22 \\
    l. & \textipa{j@-\underline{sBr}-o} & \textipa{j@sB1ro} & 0.34 & 0.73 \\ \hline
    \multicolumn{5}{c}{Fall-Fall: [CC\textipa{1}C]} \\ \hline
    m. & \textipa{j@-rfk-o} & \textipa{j@nf1ko} & 2.03 & 2.11 \\ 
    n. & \textipa{j@-rmd-o} & \textipa{j@rm1do} & 1.89 & 2.36 \\ 
    o. & \textipa{j-a-mst-o}& \textipa{jams1to} & 2.03 & 2.11 \\ \hline
    \multicolumn{5}{c}{\{Rise,Plateau\}-Fall: [C\textipa{1}CC]} \\ \hline
    p. & \textipa{j@-kft-o} & \textipa{j@k1fto} & 0.59 & 2.11 \\
    q. & \textipa{j@-dmd-o} & \textipa{j@d1mdo} & 0.27 & 2.36 \\
    r. & \textipa{j@-drs-o} & \textipa{j@d1rso} & 0.12 & 2.21 \\ 
    s. & \textipa{j@-\underline{k'rm}-o} & \textipa{j@k'1rmo} & 0.12 & 1.89 \\ 
    t. & \textipa{j@-\underline{srB}-o}  & \textipa{j@s1rBo}  & 0.22 & 1.57 \\
    u. & \textipa{j@-frt-o} & \textipa{j@f1rto} & 0.22 & 2.36 \\
    v. & \textipa{j@-sBx-o} & \textipa{j@s1Bxo} & 0.34 & 2.17 \\
    w. & \textipa{j-a-mrg-o} & \textipa{jam1rgo} & 0.46 & 2.36 \\ \hline
    \multicolumn{5}{c}{Non-jussive forms} \\ \hline
    x. & \textipa{j-t-Bt'@b@t'} & \textipa{j1t1Bt'@b@t'} & 0.18 & 2.38 \\
    y. & \textipa{j-t-rs@n@s} & \textipa{j1t1rs@n@s} & 0.12 & 2.21 \\
    z. & \textipa{j-t-kB@s@s} & \textipa{j1tk1B@s@s} & 1.37 & 0.12 \\
    A. & \textipa{j-t-k't'@k'@t'} & \textipa{j1tk'1t'@k'@t'} & 1.37 & 1.37 \\
\end{tabular}

@@

\begin{tabular}{ccccc}
	& Underlying form      & Surface form & {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) & {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) \\ \hline
    \multicolumn{5}{c}{Fall-\{Rise, Plateau\}: [CC\textipa{1}C]} \\ \hline
	a. & \textipa{j@-rk't'-o} & \textipa{j@nk'1t'o} & 2.36 & 1.37 \\
	b. & \textipa{j@-rks-o}   & \textipa{j@nk1so}   & 2.36 & 0.59 \\
    c. & \textipa{j@-rk'm-o}  & \textipa{j@nk'1mo}  & 2.36 & 0.27 \\
    d. & \textipa{j@-\underline{wzf}-o} & \textipa{j@wz1fo} & 2.03 & 1.33 \\
	e. & \textipa{j@-mxr-o}   & \textipa{j@mx1ro}   & 2.03 & 0.22 \\
    f. & \textipa{j@-\underline{sgd}-o} & \textipa{j@sg1do}   & 2.11 & 1.37 \\  
    g. & \textipa{j@-sdB-o}   & \textipa{j@sd1Bo}   & 2.11 & 0.18 \\ \hline
    \multicolumn{5}{c}{\{Rise, Plateau\}-\{Rise, Plateau\}: [C\textipa{1}CC]} \\ \hline
    h. & \textipa{j@-\underline{gdf}-o} & \textipa{j@g1dfo} & 1.37 & 0.59 \\
    i. & \textipa{j@-\underline{gdr}-o} & \textipa{j@g1dro} & 1.37 & 0.12 \\
    j. & \textipa{j@-\underline{kmr}-o} & \textipa{j@k1mro} & 0.27 & 0.46 \\
    k. & \textipa{j@-\underline{sfr}-o} & \textipa{j@s1fro} & 1.33 & 0.22 \\
    l. & \textipa{j@-\underline{sBr}-o} & \textipa{j@s1Bro} & 0.34 & 0.73 \\ \hline
    \multicolumn{5}{c}{Fall-Fall: [CC\textipa{1}C]} \\ \hline
    m. & \textipa{j@-rfk-o} & \textipa{j@nf1ko} & 2.03 & 2.11 \\ 
    n. & \textipa{j@-rmd-o} & \textipa{j@rm1do} & 1.89 & 2.36 \\ 
    o. & \textipa{j-a-mst-o}& \textipa{jams1to} & 2.03 & 2.11 \\ \hline
    \multicolumn{5}{c}{\{Rise,Plateau\}-Fall: [C\textipa{1}CC]} \\ \hline
    p. & \textipa{j@-kft-o} & \textipa{j@k1fto} & 0.59 & 2.11 \\
    q. & \textipa{j@-dmd-o} & \textipa{j@d1mdo} & 0.27 & 2.36 \\
    r. & \textipa{j@-drs-o} & \textipa{j@d1rso} & 0.12 & 2.21 \\ 
    s. & \textipa{j@-\underline{k'rm}-o} & \textipa{j@k'1rmo} & 0.12 & 1.89 \\ 
    t. & \textipa{j@-\underline{srB}-o}  & \textipa{j@s1rBo}  & 0.22 & 1.57 \\
    u. & \textipa{j@-frt-o} & \textipa{j@f1rto} & 0.22 & 2.36 \\
    v. & \textipa{j@-sBx-o} & \textipa{j@s1Bxo} & 0.34 & 2.17 \\
    w. & \textipa{j-a-mrg-o} & \textipa{jam1rgo} & 0.46 & 2.36 \\ \hline
\end{tabular}

@@

	\node (TR) at (0.124354994547*8, 1) {TR};
	\node (Tb) at (0.183110817262*8, 0.5) {T\textipa{B}};
	\node (FR) at (0.218668945874*8, 1) {FR};
	\node (TN) at (0.266252049151*8, 1.5) {TN};
	\node (Fb) at (0.343023940421*8, 1) {F\textipa{B}};
	\node (NR) at (0.463647609001*8, 1) {NR};
	\node (FN) at (0.540419500271*8, 0.5) {FN};
	\node (TF) at (0.588002603548*8, 1) {TF};
	\node (bR) at (0.726642340682*8, 0.5) {\textipa{B}R};
	\node (Nb) at (0.785398163397*8, 1) {N\textipa{B}};
	\node (RR) at (1.10714871779*8, 1) {RR};
%	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
	\node (NN) at (1.2490457724*8, 1) {NN};
	\node (FF) at (1.32581766367*8, 1.5) {FF};
	\node (TT) at (1.37340076695*8, 1) {TT};
	\node (Rb) at (1.57079632679*8, 1) {R\textipa{B}};
	\node (bN) at (1.65393755868*8, 0.5) {\textipa{B}N};
	\node (RN) at (1.84*8, 1) {RN}; %1.89254688119
	\node (NF) at (2.0344439358*8, 1) {NF};
%	\node (GF) at (2.0344439358*8, 1.5) {GF};
	\node (FT) at (2.11121582707*8, 0.5) {FT};
	\node (bF) at (2.17308367293*8, 1) {\textipa{B}F};
	\node (RF) at (2.21429743559*8, 1.5) {RF};
	\node (RT) at (2.35619449019*8, 1) {RT};
	\node (NT) at (2.35619449019*8, 0.5) {NT};
	\node (bT) at (2.38057989937*8, 1.5) {\textipa{B}T};
  \node (rising) at (0.3*8,2.3) {\underline{Rising sonority}};
  \node (level) at (1.2*8,2.3) {\underline{Level sonority}};
  \node (falling) at (2.2*8,2.3) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,0) {};
  \node (axisend)   at (2.7*8,0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
  \node (0pointlabel) at (0.0,-0.5) {0};
  \node (1pointlabel) at (1.0*8,-0.5) {1};
  \node (2pointlabel) at (2.0*8,-0.5) {2};
  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
  % dividing line
  \node (dividinglinestart) at (1.9 * 8,2) {};
  \node (dividinglineend)   at (1.9 * 8,-0.3) {};
  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
  \node (dividingpointlabel) at (1.9*8, -0.5) {1.9};
  \node (dividingpointlabel2) at (1.9*8, -1.0) {\ref{CRNidiolect}};
  % another dividing line
  \node (dividingline2start) at (1.5 * 8,2) {};
  \node (dividingline2end)   at (1.5 * 8,-0.3) {};
  \path [line,dashed] (dividingline2start) -- (dividingline2end) -- cycle;
  \node (dividingpoint2label) at (1.5*8, -0.5) {1.5};
  \node (dividingpoint2label2) at (1.5*8, -1.0) {\ref{defaultCCCidiolect} \& \ref{C1CCidiolect}};
  % third dividing line
  \node (dividingline3start) at (1.0 * 8,2) {};
  \node (dividingline3end)   at (1.0 * 8,-0.3) {};
  \node (dividingpoint3label) at (1.0*8, -1.0) {\ref{wizfidiolect}};
  \path [line,dashed] (dividingline3start) -- (dividingline3end) -- cycle;

\end{tikzpicture}
}

@@

\bigskip
\resizebox{\linewidth}{!}{
\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
  \tikzstyle{line} = [draw, -latex']
  \node (RT) at (2.5*8, 0)  {RT};
  \node (NT) at (1.67*8,0)  {NT};
  \node (FT) at (1.25*8,0)  {FT};
  \node (TT) at (1*8,-0.5)     {TT};
  \node (RF) at (2*8,0)     {RF};
  \node (NF) at (1.33*8,-0.5)  {NF};
  \node (FF) at (1*8,0)   {FF};
  \node (TF) at (0.8*8,-0.5)   {TF};
  \node[draw,circle,dashed] (RN) at (1.5*8,0)   {RN};
  \node (NN) at (1*8,0.5)     {NN};
  \node (FN) at (0.75*8,0)  {FN};
  \node (TN) at (0.6*8,0)   {TN};
  \node (RR) at (1*8,1.0)  {RR};
  \node (NR) at (0.67*8,-0.5)  {NR};
  \node (FR) at (0.5*8,0)   {FR};
  \node (TR) at (0.4*8,0)   {TR};
  \node (rising) at (0.5*8,2) {\underline{Rising sonority}};
  \node (level) at (1*8,2) {\underline{Level sonority}};
  \node (falling) at (1.67*8,2) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,-1.0) {};
  \node (axisend)   at (2.7*8,-1.0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, -1.2) -- (0.0*8, -0.8) -- cycle;
  \draw (1.0*8, -1.2) -- (1.0*8, -0.8) -- cycle;
  \draw (2.0*8, -1.2) -- (2.0*8, -0.8) -- cycle;
  \node (0pointlabel) at (0.0,-1.5) {0};
  \node (1pointlabel) at (1.0*8,-1.5) {1};
  \node (2pointlabel) at (2.0*8,-1.5) {2};
  \node (xaxislabel) at (2.7*8,-1.5) {\textsc{SonRise}};

  % third dividing line
  \node (dividingline3start) at (1.15 * 8,1.5) {};
  \node (dividingline3end)   at (1.15 * 8,-1.5) {};
  \path [line,dashed] (dividingline3start) -- (dividingline3end) -- cycle;
\end{tikzpicture}
}
\bigskip

@@

In this section, I will demonstrate that the four rankings already obtained in $\S$\ref{CCCanalysis} for the triconsonantal clusters predict almost exactly which of the quadriconsonantal clusters should display variation, and in which direction.

The following table shows the observed behaviour of the quadriconsonantal clusters of Chaha, as reported by \cite{rose.2000}.

\ex. Epenthetic behaviour of CCCC clusters

\begin{center}
\begin{tabular}{|cc|c|} \hline
   & Underlying form & Observed surface forms \\ \hline
 a.& \textipa{sdBn} & \textipa{sd1Bn} \\ 
 b.& \textipa{wzfn} & \textipa{wz1fn}, \textipa{w1zf1n} \\
 c.& \textipa{gdfn} & \textipa{gd1fn}, \textipa{g1df1n} \\
 d.& \textipa{mstn} & \textipa{m1st1n} \\
 e.& \textipa{dmdn} & \textipa{d1md1n} \\
 f.& \textipa{drsn} & \textipa{d1rs1n} \\
 g.& \textipa{sBxn} & \textipa{s1Bx1n} \\
 h.& \textipa{kftn} & \textipa{k1ft1n}  \\
 i.& \textipa{ktfn} & \textipa{kt1fn}, \textipa{k1tf1n} \\
 j.& \textipa{sgdn} & \textipa{sg1dn}, \textipa{s1gd1n} \\
 k.& \textipa{srBn} & \textipa{sr1Bn}, \textipa{s1rB1n} \\
 l.& \textipa{krmn} & \textipa{kr1mn}, \textipa{k1rm1n}  \\ \hline
 \end{tabular}
\end{center}

@@

Therefore, the only two possible solutions under my approach are [CC\textipa{1}CC] and [C\textipa{1}CC\textipa{1}C]. Which one is chosen depends on the sonority profile of the clusters, and which of Rose's constraints {\sc Align-Left} and {\sc Anchor-Left Root} is dominant.

@@

\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c:c|} \hline 
\multicolumn{3}{|c||}{Input:~/\textipa{n-\textnormal{CCC}-n@}/} & Align-Left & Anchor-Left Root \\[0.5ex]
\hline \hline a. & & \textipa{n1\textnormal{C.C}1\textnormal{C}.n@} & 2,3,5,6 & $\ast$! \\
\hline b. & \ding{43} & \textipa{n1.\textnormal{C}1\textnormal{C.C}1.n@} & 2,4!,5,7 & \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}

@@

In this paper, I argued for sonority contour faithfulness being the right way to analyse sonority-driven epenthesis, giving case studies in Irish and Chaha as examples. I additionally proposed that sonority contour distance should be computed by a metric that obeys two desiderata:

\ex. Desiderata for a sonority contour faithfulness metric 
     \a. The more positive the gradient of the sonority contour from C\textsubscript{1} to C\textsubscript{2}, the smaller the faithfulness cost. 
     \b. For a given sonority distance between C\textsubscript{1} and C\textsubscript{2}, the more sonorous C\textsubscript{1} and C\textsubscript{2} are, the smaller the faithfulness cost.

@@

In Chaha, we saw more generally that the family of {\sc Ident(Son$\measuredangle$)}$<$n constraints, coupled with standard syllabic markedness constraints and alignment/anchor constraints preferring epenthesis on the left or right, yielded the complex and variable system of epenthesis positioning in the language with only one error in predictions, making it comparably successful to the existing Syllable Contact-based analysis by \cite{rose.2000}.
